% Thesis Acknowledgements ------------------------------------------------

\begin{acknowledgements}
Five years ago, the opportunity to conduct meaningful and clinically impactful brain research seemed a far off pipe dream. First and foremost, I thank my advisor and mentor, Brian Litt, for placing his trust in me and inviting me to pursue Master's and Doctoral-level research. Brian, I am indebted to you for showing me how to ask big-picture questions and instilling in me the grander vision of conducting research to help patients in the near-term. You encouraged my intellectual curiosity and afforded me the freedom to explore new domains of scientific work -- in hopes that we would understand just a little bit more about epilepsy and its complexity. You also provided me an important glimpse of academic life as a teacher and showed me how to advise younger students on harnessing their skills and pursuing meaningful careers. As a team player who humbly distributes credit in times of success, you have imprinted on me a passion for collaborative research and integrating knowledge across discplines.

Brian also deserves credit for introducing me to my second mentor, Danielle Bassett, who has played an instrumental role guiding the technical aspects of my work. Dani, your willingness and enthusiasm to discuss theory, absurd hypotheses, research papers, and academic life is a model for the type of academician I can only dream of becoming. Most importantly, you've taught me that being an excellent researcher requires more than good technical skill and vision -- it requires artistry in effective communication and language.

I would also like to extend gratitude to Timothy Lucas, for providing added perspective outside of the computational lab, in the operating room. As a neurosurgeon, you opened my eyes to a second world of clinical challenges associated with translational research, especially in epilepsy. I appreciate your patience with our Neuralynx team and thank you for valuable clinical and technical insights to overcome critical hurdles.

I would be remiss not to mention Gershon Buchsbaum as an invaluable mentor early in my dissertation work. You helped me navigate the program goals and milestones, and encouraged me to ask questions, to be thorough, and to verify hypotheses. I owe much of my thesis focus in examining spatial distributions of epileptic activity to our early discussions.

I must also thank the clinicians -- Kate Davis, Shawniqua Williams, Stephanie Chen, Brian Oommen, and Mesha-Gay Brown -- who have provided helpful discussion and devoted extended time to marking seizures in the 22 patient data set analyzed in this thesis.

Furthermore, I thank Tyler Blevins for all his time and effort in organizing and automating the analysis of these large data sets on the IEEG Portal. To say the least, without the continuous effort by Jacqueline Boccanfuso, John Frommeyer and Joost Wagenaar in actively maintaining the IEEG infrastructure, the valuable patient data for this thesis might still be sitting in archived hospital servers.

Carolyn Wilkinson, Ruth Krieger, Jacqueline Boccanfuso, and Ashley Brito deserve many thanks in their many hats as data coordinators, proofreaders, event planners and all-in-all making the lab run as smooth as butter.

I especially thank Hank Bink, Lohith Kini, and Hoameng Ung, who have become close friends. Hank, the tall guy sitting directly to my left, has been my source of comic relief and my teacher of pop culture over the last five years. I also thank my close friends outside of lab for helping me maintain a healthy work-life balance.

Mom, Dad, and Kaushal -- your life-long support and love is the only reason I have made it to where I am. You have all stuck behind me, even through my most stubborn times, and no words can express the amount of gratitude I feel. Finally, Kinjal, you balance my insanity with your sanity and poise. Even on the grimmest days of my PhD, you managed to keep me going with all smiles. If the past few years are any indication, this is just the start of a great adventure with you.

\end{acknowledgements}

% ------------------------------------------------------------------------


